SCM plan for a troubling company

### 2012-01-11 article.tex
Added example bibtexing

\documentclass[a4paper,11pt]{article}
\usepackage[utf8x]{inputenc}

@@

As the company hasn̈́'t used any form of SCM-tool previously explicit branching didn't exist.
The copying of code between subgroups working on different modules however created implicit branches whenever two version weren't in sync. This creates an implicit feature branch model with merges at each release and sometimes in between but not very often as those merges are hard to

@@

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage{cite}

@@

As the company hasn̈́'t used any form of SCM-tool previously explicit branching didn't exist.
The copying of code between subgroups working on different modules however created implicit branches whenever two version weren't in sync. This creates an implicit feature branch model with merges at each release and sometimes in between but not very often as those merges are hard to do and requires that all of the changes made by the other team be merged together with the needed features/changes. This makes the merges very hard to do when it's finally time to do so and is the cause of the long merging periods/missed deadlines.

The sporadic merges also gives a composition model but where the choices to make a composition of are very limited leading to collaboration

@@

\bibliography{refs}
\bibliographystyle{plain}
